### 2022-05-18 supplement.Rmd
Fix sensitivity analysis

  # Create table for the meta-analysis of mental rotation performance
  sens %>%
    select(res, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res, manipulation_name, manipulation_value) {
      print_res_table(
        res,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs7
  write_tsv(tabs7, file = here(tables_dir, "tabs7_sens_meta.tsv"))

>>>>

  # Create table for the meta-analysis of mental rotation performance
  sens %>%
    select(res_meta, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res_meta, manipulation_name, manipulation_value) {
      print_res_table(
        res_meta,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs7
  write_tsv(tabs7, file = here(tables_dir, "tabs7_sens_meta.tsv"))
